### 2016-07-10 Virt_Real.tex
text in NLO chapter

\subsubsection{Real Quark Radiation}
As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences. However, there is a further contribution to squark production at next-to-leading order. This involves the radiation of an additional antiquark in the final state. To meet color conservation, the initial state has to be composed of a quark and a gluon, see fig. \ref{fig:quarkradiation}.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
\begin{scope}[shift={(0,0.25)}]
	\draw[fermion] (-1.25,0.75)--(-0.5,0);
	\draw[gluon] (-1.25,-0.75)--(-0.5,0);
	\draw[fermion] (-0.5,0)--(0.5,0); 
	\draw[scalar] (0.5,0)--(1.25,0.75);
	\draw[gluon] (0.5,0)--(1.25,-0.75);
	\draw[fermionnoarrow] (0.5,0)--(1.25,-0.75);
	\draw[scalar] (1.25,-0.75)--(2,0);
	\draw[fermion] (2,-1.5)--(1.25,-0.75);
	\end{scope}
\begin{scope}[shift={(3,0)}]
	\draw[fermion] (0,1)--(1,1);	
	\draw[gluon] (0,-0.5)--(1,-0.5);
	\draw[fermionnoarrow] (1,1)--(1,-0.5);
	\draw[gluon] (1,1)--(1,-0.5);
	\draw[scalar] (1,1)--(2.75,1);
	\draw[fermionnoarrow] (1,-0.5)--(2,-0.5);
	\draw[gluon] (1,-0.5)--(2,-0.5);
	\draw[scalar] (2,-0.5)--(2.75,0.25);
	\draw[fermion] (2.75,-1.25)--(2,-0.5);
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermion] (0,1)--(1,1);
	\draw[gluon] (0,-1)--(1,-1);
	\draw[fermionnoarrow] (1,1)--(1,0);
	\draw[gluon] (1,1)--(1,0);
	\draw[fermion] (1,-1)--(1,0);
	\draw[scalar] (1,1)--(2,1);
	\draw[fermion] (2,-1)--(1,-1);
	\draw[scalar] (1,0)--(2,0);
\end{scope}
\end{tikzpicture}
\caption{A selection of real quark emission diagrams contributing to squark production. The first two diagrams have a gluino propagator which may go on-shell. In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\label{fig:quarkradiation}
\end{center}
\end{figure}
These contributions do not comprise soft divergences. A split-up of space space in a soft and a hard part is therefore not needed. However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of \ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
But there is another complication: The first and second diagram in fig. \ref{fig:quarkradiation} include a gluino which subsequently decays into a squark-antiquark pair. If the squared gluino's four-momentum approaches its mass-shell $p^2 = m^2_{\tilde{g}}$ the amplitude of this diagram hits a singularity. Of course, this can only happen if $m_{\tilde{g}} > m_{\tilde{q}}$.\\
These singularities are treated by introducing a non-zero width $\Gamma_{\tilde{q}}$ for the gluino as a regulator, i.e. modifying the propagator to the Breit-Wigner form
\begin{align}
\frac{1}{p^2 - m_{\tilde{q}}^2} \to \frac{1}{p^2 - m_{\tilde{q}}^2 + i m_{\tilde{q}} \Gamma_{\tilde{q}}}.
\end{align}
Integrating over the regime of phase space, where the gluino approaches its mass-shell, actually gives the tree-level contribution of the process $qG \to \tilde{q}\tilde{g}$ weighted by the branching ratio $\frac{\Gamma_{\tilde{q}\to q \tilde{g}}}{\Gamma_{\tilde{q}}}$. To avoid double counting, one has to cut this very regime of phase space out and subtract it from the total contribution originating from those diagrams. For a detailed prescription on how to deal with this issue, see \cite{Beenakker:1996ch, Gavin:2013kga}.

>>>>

\subsubsection{Real Quark Radiation}\ref{sec:RealQuarkRad}
As already mentioned before, adding up virtual and real gluon emission contributions results in the cancellation of divergences. However, there is a further contribution to squark production at next-to-leading order. This involves the radiation of an additional antiquark in the final state. To meet color conservation, the initial state has to be composed of a quark and a gluon, see fig. \ref{fig:quarkradiation}.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
\begin{scope}[shift={(0,0.25)}]
	\draw[fermion] (-1.25,0.75)--(-0.5,0);
	\draw[gluon] (-1.25,-0.75)--(-0.5,0);
	\draw[fermion] (-0.5,0)--(0.5,0); 
	\draw[scalar] (0.5,0)--(1.25,0.75);
	\draw[gluon] (0.5,0)--(1.25,-0.75);
	\draw[fermionnoarrow] (0.5,0)--(1.25,-0.75);
	\draw[scalar] (1.25,-0.75)--(2,0);
	\draw[fermion] (2,-1.5)--(1.25,-0.75);
	\end{scope}
\begin{scope}[shift={(3,0)}]
	\draw[fermion] (0,1)--(1,1);	
	\draw[gluon] (0,-0.5)--(1,-0.5);
	\draw[fermionnoarrow] (1,1)--(1,-0.5);
	\draw[gluon] (1,1)--(1,-0.5);
	\draw[scalar] (1,1)--(2.75,1);
	\draw[fermionnoarrow] (1,-0.5)--(2,-0.5);
	\draw[gluon] (1,-0.5)--(2,-0.5);
	\draw[scalar] (2,-0.5)--(2.75,0.25);
	\draw[fermion] (2.75,-1.25)--(2,-0.5);
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermion] (0,1)--(1,1);
	\draw[gluon] (0,-1)--(1,-1);
	\draw[fermionnoarrow] (1,1)--(1,0);
	\draw[gluon] (1,1)--(1,0);
	\draw[fermion] (1,-1)--(1,0);
	\draw[scalar] (1,1)--(2,1);
	\draw[fermion] (2,-1)--(1,-1);
	\draw[scalar] (1,0)--(2,0);
\end{scope}
\end{tikzpicture}
\caption{A selection of real quark emission diagrams contributing to squark production. The first two diagrams have a gluino propagator which may go on-shell. In this regime of phase space these diagrams should not be included in the correction to squark-production but to a tree-level contribution to squark-gluino-production.}\label{fig:quarkradiation}
\end{center}
\end{figure}
These contributions do not comprise soft divergences. A split-up of space space in a soft and a hard part is therefore not needed. However, there are collinear singularities, originating from initial state radiation like shown in the last diagram of \ref{fig:quarkradiation}, which again have to be removed by means of mass factorization.\\
But there is another complication: The first and second diagram in fig. \ref{fig:quarkradiation} include a gluino which subsequently decays into a squark-antiquark pair. If the squared gluino's four-momentum approaches its mass-shell $p^2 = m^2_{\tilde{g}}$ the amplitude of this diagram hits a singularity. Of course, this can only happen if $m_{\tilde{g}} > m_{\tilde{q}}$.\\
These singularities are treated by introducing a non-zero width $\Gamma_{\tilde{q}}$ for the gluino as a regulator, i.e. modifying the propagator to the Breit-Wigner form
\begin{align}
\frac{1}{p^2 - m_{\tilde{q}}^2} \to \frac{1}{p^2 - m_{\tilde{q}}^2 + i m_{\tilde{q}} \Gamma_{\tilde{q}}}.
\end{align}
Integrating over the regime of phase space, where the gluino approaches its mass-shell, actually gives the tree-level contribution of the process $qG \to \tilde{q}\tilde{g}$ weighted by the branching ratio $\frac{\Gamma_{\tilde{q}\to q \tilde{g}}}{\Gamma_{\tilde{q}}}$. To avoid double counting, one has to cut this very regime of phase space out and subtract it from the total contribution originating from those diagrams. For a detailed prescription on how to deal with this issue, see \cite{Beenakker:1996ch, Gavin:2013kga}.
